Concurrent Programming in Harmony

### 2021-12-25 book/paper.tex
Pass over Ch 23 and 24

<{:const:net_send}>
<{:const:net_recv}>
<{:const:app_send}>
<{:const:app_recv}>
<{:const:send}>
<{:const:receive}>
<{:const:processor}>
<{:const:broadcast}>

@@

It is useful to create an abstract network that reliably sends messages
between threads, much like the FIFO queue in the <{synch}> module.
For this, we need a network protocol that Alice and Bob can run.
In particular, it has to be the case that if Alice sends application
messages $m_1, ..., m_n$ in that order, then if Bob receives an
application message
<{m}>, then $m = m_i$ for some <{i}> and Bob will already have received
application messages $m_1, ..., m_i$ (safety).
Also, if the network is fair and Alice sends application message
<{m}>, then eventually Bob should deliver <{m}> (liveness).

>>>>

<{:module:abp}>
<{:const:net_send}>
<{:const:net_recv}>
<{:const:app_send}>
<{:const:app_recv}>
<{:const:send}>
<{:const:receive}>
<{:const:processor}>
<{:const:broadcast}>

@@

It is useful to create an abstract network that reliably sends messages
between threads, much like the FIFO queue in the <{synch}> module.
For this, we need a network protocol that Alice and Bob can run.
In particular, it has to be the case that if Alice sends application
messages $m_1, ..., m_n$ in that order, then if Bob receives an
application message
<{m}>, then $m = m_i$ for some <{i}> and, unless $m$ is the very first
message, Bob will already have received
application messages $m_1, ..., m_{i-1}$ (safety).
Also, if the network is fair and Alice sends application message
<{m}>, then eventually Bob should deliver <{m}> (liveness).
